The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-13 albatros_paper.tex
HCC added jpg version of synthesized beam image, with trimmed margins
HCC added a few sentences and references about RRLs

\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\jgr}{Journal of Geophysical Research}
\newcommand{\pasa}{Publications of the Astronomical Society of Australia}
\newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
\newcommand{\prd}{Physical Review D}
\newcommand{\prl}{Physical Review Letters}

@@

Very few experiments have surveyed the radio sky at $\lesssim 30$~MHz,
and here, we highlight only four specific examples.  At the very
lowest frequencies, the state of the art among ground-based
measurements dates from the 1950s, when Reber and Ellis caught brief
glimpses of the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an
array of 192~dipoles~\citep{1956JGR....61....1R}.  A few space-based
missions have also performed measurements at similarly low frequency
ranges; for example, the Radio Astronomy Explorer-2 operated at
\SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  The first step
toward laying the groundwork for possible measurements of the dark
ages is obtaining an improved map of Galactic foregrounds at $\lesssim
30$~MHz.  In addition to serving as a stepping stone for future
cosmological constraints from the dark ages, maps at these frequencies
can also shed new light on Galactic astrophysics.  Above $\sim30$~MHz,
synchrotron emission from the Galaxy follows a power law with a
frequency dependence of $\nu^{-5/2}$.  At lower frequencies,
synchrotron self-absorption becomes non-negligible, and the spectrum
transitions to $\nu^{5/3}$ dependence.  Since self-absorption causes
the optical depth along the line of sight to depend on frequency,
observations at $\lesssim 30$~MHz have the potential to probe the
three-dimensional cosmic ray structure of the
Galaxy~\citep{2002ApJ...575..217P}.

\attention{Words here about radio recombination lines.}
\attention{More words here about possible ionospheric studies.}

% Words here about space-based concepts, and more words about doing
% what we can from the ground first

@@

>>>>

\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\jgr}{Journal of Geophysical Research}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\nar}{New Astronomy Reviews}
\newcommand{\pasa}{Publications of the Astronomical Society of Australia}
\newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
\newcommand{\prd}{Physical Review D}
\newcommand{\prl}{Physical Review Letters}

@@

Very few experiments have surveyed the radio sky at $\lesssim 30$~MHz,
and here, we highlight only four specific examples.  At the very
lowest frequencies, the state of the art among ground-based
measurements dates from the 1950s, when Reber and Ellis caught brief
glimpses of the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an
array of 192~dipoles~\citep{1956JGR....61....1R}.  A few space-based
missions have also performed measurements at similarly low frequency
ranges; for example, the Radio Astronomy Explorer-2 operated at
\SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  The first step
toward laying the groundwork for possible measurements of the dark
ages is obtaining an improved map of Galactic foregrounds at $\lesssim
30$~MHz.  In addition to serving as a stepping stone for future
cosmological constraints from the dark ages, maps at these frequencies
can also shed new light on Galactic astrophysics.  Above $\sim30$~MHz,
synchrotron emission from the Galaxy follows a power law with a
frequency dependence of $\nu^{-5/2}$.  At lower frequencies,
synchrotron self-absorption becomes non-negligible, and the spectrum
transitions to $\nu^{5/3}$ dependence.  Since self-absorption causes
the optical depth along the line of sight to depend on frequency,
observations at $\lesssim 30$~MHz have the potential to probe the
three-dimensional cosmic ray structure of the
Galaxy~\citep{2002ApJ...575..217P}.  Low-frequency observations can
also be used to image radio recombination lines (RRLs), which provide
a means for studying cool, low-density regions of the interstellar
medium (ISM).  These absorption lines arise from Rydberg atoms and are
highly sensitive to the surrounding environment.  The RRL spectrum and
absorption profiles can therefore constrain the detailed properties of
the ISM regions in which the Rydberg atoms are
formed~\citep{2009NewAR..53..259G, 2007MNRAS.374..852S}.

\attention{Words here about possible ionospheric studies.}

\attention{Words here about space-based concepts and complementarity
  with ground-based measurements.}

@@

We are extremely grateful for the anemic carrots on Marion.  Yum.
